\section{Our Experiment}
\subsection{Infrastructure}
\subsubsection{Apache Spark}
\paragraph{}Apache spark is the new trend on distributed computation and map-reduce. 
But first things first, what is map-reduce. \\\\
What is map reduce\\

Spark's predecessor, hadoop map reduce, was for a long time at its peak. Hadoop map reduce, is a distributed map-reduce system, this means that it has a mechanism to distribute work on nodes and a common interface for handling data. In hadoop's case this was able to happen due to Apache hadoop yarn and the HDFS (hadoop distributed file system). When a job was scheduled, data were loaded by the hdfs to a worker, then the worker was putting the result back to the hdfs. 
\\\\
Important note: cite apache hadoop yarn https://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html
\\\\
Important note: add architecture diagrams for both hadoop and spark --> note the common parts of HDFS and YARN
\\\\
But innovation knocked the door and resilient distributed datasets entered the room. In spark world, data are loaded to hdfs as before. Then spark loads them in an RDD, this means that data are now accessible on each machine's memory. Any transformation done to a RDD results a RDD, and so forth. After all the transformations are done, spark can transform the results to a file in hdfs.
\\\\
How spark differentiates from its predecessors, hadoop yarn\\
Spark lightweight in memory data transformation 
Resilient Distributed Datasets (RDDs) \\
mllibs\\
add spark jira note \\\\
Important note: mention als distributed broadcasting implementation. 
\\\\
broadcasting rdd \\
//cite the mastering apache spark book
\cite{ApacheSpark:1} \\
a Spark cluster to be created on AWS EC2 storage.\\
New trends on spark https://github.com/apache-spark-on-k8s/spark cite this repository too.
\subsection{Dataset}
What is the dataset about. This dataset contains users, movies and the rating user made about the movies.
This dataset is splited to multiple subsets of 80000 training sets and respective 20000 reviews.
\cite{MovieLens:3}
\subsection{Metrics}
\subsubsection{Mean Absolute Error}
As metrics are commonly used the MSE, RMSE and MAE. Due to the fact that the author prefers the last one, MAE was used in this experiment.
\begin{equation}
MAE = \frac{\sum_{i=1}^{n}{|y_{i}-x_{i}|} }{n} = \frac{\sum_{i=1}^{n}\sqrt{{(y_{i}-x_{i})}^{2}}}{n}
\end{equation}
\subsubsection{Execution Time}
Time is measured in milliseconds.
Execution time is always a measure when we are comparing algorithms. Even more if those algorithms execution time is heavily dependent to their complexity.