\documentclass[10pt,journal]{IEEEtran}
\usepackage{url}
\usepackage{graphicx}
\usepackage{csvsimple}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepgfplotslibrary{groupplots}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{listings}
\usepackage{setspace}
\usepackage[utf8]{inputenc}

\tikzset{
	font={\fontsize{9pt}{12}\selectfont}
	}

\begin{document}
	
	\title{Recommender Systems} % to be concidered
	\author{
		\IEEEauthorblockN{Vasileios~Simeonidis,~Dimitris~Poulopoulos,~Dimosthenis~Kiriazis}
		\IEEEauthorblockA{\\School of Information and Communication Technologies\\
			Department of Digital Systems\\
			University of Piraeus\\
			Email: vsimeonidis@outlook.com,~jim.a.ver@gmail.com,~dimos@unipi.gr}

		}

	\maketitle
	\begin{abstract}
		The last decade Internet has been flooded with information. Information that nobody can filter, nobody can find what he needs. From raw data, videos, music or products surrounds each user. Large retail sites like Amazon developed recommender systems in order to offer products to their users. The need although is not limited only in the retail area. 
		
		Web sites like Youtube or Vimeo need to recommend to each user of their, videos that may like to watch next. Facebook is another example of an application utilizing lots of data and offering recommendations on what you may want to read or who may be a friend of yours. Most of the times, a recommender system is not the core functionality of an application. It is through a very useful feature that gives a clear advantage in any business area needed.
		
		This paper aims to distinguishe metrics on recommender systems  that can be proved useful to compare them. Also, this paper, performs a comparison between two algorithms of the collaborative filtering family. The content based with focus on items and the machine learning oriented alternating least square (als).
	\end{abstract}
	\begin{IEEEkeywords}
		Recommender Systems, Collaborative filtering, Alternating Least Squares
	\end{IEEEkeywords}

	
%	\tableofcontents
%	\listoftables
%	\newpage
%	\listoffigures
	\pagenumbering{arabic}
	\input{intro.tex}
	\input{collaborativeFiltering.tex}
	\input{experiment.tex}
	\input{results.tex}
	\input{conclusion.tex}


%\section*{Acknowledgements}
%This work couldn't be completed without the great support I received from so many people over this year. I would like to thank the following people.
%
%My supervisor Dr. Dimosthenis Kyriazis for totally supporting me in the choices I made and giving me the freedom I was needing.
%
%My friend and fellow student Dimitris Poulopoulos for helping me understand the field of recommender systems and supported me technically and theoretically.
%
%My friends and colleagues George Adamopoulos and Nikos Silvestros for constantly teaching me high-level engineering and scientific thinking. Also, I would like to thank them for putting the right amount of pressure on me in order to complete this thesis.
%
%Kronos, the development team I am part of and helping me to keep my spirit high. Thank you, Apostolos Chissas, Kostas Rigas, Christos Grivas, Peter Lengos, Vasiliki Giamarelou, Maria Karkeli, Eleni Karakizi, Spyros Argyroiliopoulos, Nikos Anagnostou and Ioannis Koutsileos. 
%
%Last but not least, I would like to thank my close friends and family for bearing me while I was anxious about the completion of this thesis.
	
	\bibliography{paper}
	\bibliographystyle{ieeetr}
\end{document}